---
title: "Supplement"
subtitle: "On the journal article ... "
author:
  - name:  Jürgen Schneider 
    url: https://uni-tuebingen.de/de/175743
    affiliation: University of Tübingen
    email: juergen.schneider@uni-tuebingen.de
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    code_folding: hide
    theme: cosmo
    highlight: espresso
css: www/style.css
editor_options: 
  chunk_output_type: console
---

# system properties

__Used packages__

```{r setup, echo=T, message=F, warning=F, comment=F}
knitr::opts_chunk$set(echo = T, message = F, warning = F)
library(rio)
library(tidyverse)
library(stringr)
library(mice)
library(miceadds)
library(naniar)
library(corrgram)
library(lavaan)
library(pander)
library(bain)
library(MASS)
library(BayesFactor)
library(ggthemes)
library(psych)
library(ggside)
```

__R-Version__

```{r rversion}
R.Version()
```

# Import data

* __Data "ZA6259_v1-0-0.sav"__
    + Get the __open data__ via the repository [https://doi.org/10.4232/1.13468](https://doi.org/10.4232/1.13468)
    + or by clicking here to `r xfun::embed_file(here::here("data_public/ZA6259_v1-0-0.sav"), text="download the Data")` that are embedded in this HTML file
* __Data "ts.Rdata"__: Click here to `r xfun::embed_file(here::here("data_public/ts.Rdata"), text="download the Data")` that are embedded in this HTML file
* __Analyses__: Github Repo [https://github.com/j-5chneider/pbl-vs-di](https://github.com/j-5chneider/pbl-vs-di)

```{r }
# this is the data you need to download from Gesis or from within this file
pbl_di <- rio::import("data_public/ZA6259_v1-0-0.sav")
```


# Wrangle data

```{r }
# construct treatment variable
# 0 = DI, 1 = PBL
pbl_di$treatment <- ifelse(c(pbl_di$seminartyp == 4 | pbl_di$seminartyp == 2), 0, 1)


# get variables on theory and selection from other data set (needs to be reintegrated into original data set)
ts <- rio::import("data_public/ts.Rdata") %>%
  dplyr::select(code, anz.komm.43.1, anz.komm.43.2, anz.komm.43.7, anz.komm.43.3, anz.komm.43.4, anz.komm.43.5, 
                theorie.r.43.1, theorie.r.43.2, theorie.r.43.7, theorie.r.43.3, theorie.r.43.4, theorie.r.43.5,
                doz_pass, doz_gef) %>%
  dplyr::mutate(code = str_trim(code))

pbl_di <- left_join(pbl_di, ts, by ="code")


# construct centered variable for attendance
pbl_di <- pbl_di %>%
  dplyr::mutate(attendance = rowSums(data.frame(anwesend_erst, anwesend_zweit)))

# anwesend_MEAN <- pbl_di %>%
#                     summarize(anwesend_M = mean(anwesend, na.rm=TRUE))

# construct variable literature
pbl_di <- pbl_di %>%
  dplyr::mutate(literature = rowSums(data.frame(T2_text_1, T2_text_2, T2_text_3)))

# construct the variable lit_pre (literature read before the treatment)
pbl_di <- pbl_di %>%
  dplyr::mutate(lit_pre = rowSums(data.frame(T1_text_1, T1_text_2, T1_text_3)))

# construct the variable prior_knowledge, 
# based on a test on declarative knowledge on classroom management
pbl_di <- pbl_di %>%
  mutate(prior_knowledge = rowMeans(data.frame(T1_wiss_crm_verh1, T1_wiss_crm_verh2, T1_wiss_crm_verh3, T1_wiss_crm_verh4, T1_wiss_crm_verh5, T1_wiss_crm_verh6, T1_wiss_crm_bez1, T1_wiss_crm_bez2, T1_wiss_crm_unt1, T1_wiss_crm_unt2, T1_wiss_crm_unt3, T1_wiss_crm_unt4, T1_wiss_crm_unt5, T1_wiss_crm_unt6), na.rm = T))


pbl_di <- pbl_di %>%
  mutate(sel_att_pre1 = case_when(
                           is.na(theorie.r.43.1) & is.na(theorie.r.43.2) & is.na(theorie.r.43.7) &
                           is.na(A43_1) & is.na(A43_2) & is.na(A43_7) ~ as.numeric(NA),
                           TRUE ~ as.numeric(anz.komm.43.1)),
         sel_att_pre2 = case_when(
                           is.na(theorie.r.43.1) & is.na(theorie.r.43.2) & is.na(theorie.r.43.7) &
                           is.na(A43_1) & is.na(A43_2) & is.na(A43_7) ~ as.numeric(NA),
                           TRUE ~ as.numeric(anz.komm.43.2)),
         sel_att_pre3 = case_when(
                           is.na(theorie.r.43.1) & is.na(theorie.r.43.2) & is.na(theorie.r.43.7) &
                           is.na(A43_1) & is.na(A43_2) & is.na(A43_7) ~ as.numeric(NA),
                           TRUE ~ as.numeric(anz.komm.43.7)),
         sel_att_post1 = case_when(
                           is.na(theorie.r.43.3) & is.na(theorie.r.43.4) & is.na(theorie.r.43.5) &
                           is.na(A43_3) & is.na(A43_4) & is.na(A43_5) ~ as.numeric(NA),
                           TRUE ~ as.numeric(anz.komm.43.3)),
         sel_att_post2 = case_when(
                           is.na(theorie.r.43.3) & is.na(theorie.r.43.4) & is.na(theorie.r.43.5) &
                           is.na(A43_3) & is.na(A43_4) & is.na(A43_5) ~ as.numeric(NA),
                           TRUE ~ as.numeric(anz.komm.43.4)),
         sel_att_post3 = case_when(
                           is.na(theorie.r.43.3) & is.na(theorie.r.43.4) & is.na(theorie.r.43.5) &
                           is.na(A43_3) & is.na(A43_4) & is.na(A43_5) ~ as.numeric(NA),
                           TRUE ~ as.numeric(anz.komm.43.5))
         )


# deleting some variables to avoid problems with imputation
pbl_di <- pbl_di %>%
  mutate(theory_pre1 = theorie.r.43.1,
         theory_pre2 = theorie.r.43.2,
         theory_pre3 = theorie.r.43.7,
         theory_post1 = theorie.r.43.3,
         theory_post2 = theorie.r.43.4,
         theory_post3 = theorie.r.43.5,
         inquiry_pre1 = A43_1, 
         inquiry_pre2 = A43_2, 
         inquiry_pre3 = A43_7, 
         inquiry_post1 = A43_3, 
         inquiry_post2 = A43_4, 
         inquiry_post3 = A43_5) %>% # rename some variables for easier understanding
  dplyr::select(treatment, seminar, attendance, 
         sel_att_pre1, sel_att_pre2, sel_att_pre3, sel_att_post1, sel_att_post2, sel_att_post3,
         theory_pre1, theory_pre2, theory_pre3, theory_post1, theory_post2, theory_post3, 
         inquiry_pre1, inquiry_pre2, inquiry_pre3, inquiry_post1, inquiry_post2, inquiry_post3, literature,
         T2_anstrS_1, T2_anstrS_2, T2_anstrS_3, T2_anstrT_1, T2_anstrT_2, T2_anstrT_3, T2_anstrT_4,
         doz_pass, doz_gef,
         geschl, unterrichtet, erf_vid, lit_pre, prior_knowledge) %>%
  dplyr::filter(!is.na(seminar))



```


# Names and labels of variables
```{r }
names_labels <- data.frame(names = names(pbl_di[1:31]),
                          `item labels` = c(
                            "Treatment variable [0: DI, 1: PBL]",
                            "ID of course group (used as cluster variable)",
                            "How many of the treatment sessions the student attended [0,1,2]",
                            "Measure of selective attention, first sequence of pre-test [quantity of comments]",
                            "Measure of selective attention, second sequence of pre-test [quantity of comments]",
                            "Measure of selective attention, third sequence of pre-test [quantity of comments]",
                            "Measure of selective attention, first sequence of post-test [quantity of comments]",
                            "Measure of selective attention, second sequence of post-test [quantity of comments]",
                            "Measure of selective attention, third sequence of post-test [quantity of comments]",
                            "Measure of theory integration, first sequence of pre-test [% of comments with theory integration: 0-100]",
                            "Measure of theory integration, second sequence of pre-test [% of comments with theory integration: 0-100]",
                            "Measure of theory integration, third sequence of pre-test [% of comments with theory integration: 0-100]",
                            "Measure of theory integration, first sequence of post-test [% of comments with theory integration: 0-100]",
                            "Measure of theory integration, second sequence of post-test [% of comments with theory integration: 0-100]",
                            "Measure of theory integration, third sequence of post-test [% of comments with theory integration: 0-100]",
                            "Measure of inquiry steps realized, first sequence of pre-test [0,1,2,3]",
                            "Measure of inquiry steps realized, second sequence of pre-test [0,1,2,3]",
                            "Measure of inquiry steps realized, third sequence of pre-test [0,1,2,3]",
                            "Measure of inquiry steps realized, first sequence of post-test [0,1,2,3]",
                            "Measure of inquiry steps realized, second sequence of post-test [0,1,2,3]",
                            "Measure of inquiry steps realized, third sequence of post-test [0,1,2,3]",
                            "number of theoretical literature on classroom management read [0,1,2,3]",
                            "Willingness for effort, Likert item 1 [1,2,3,4]",
                            "Willingness for effort, Likert item 2 [1,2,3,4]",
                            "Willingness for effort, Likert item 3 [1,2,3,4]",
                            "Willingness for effort, Likert item 4 [1,2,3,4]",
                            "Willingness for effort, Likert item 5 [1,2,3,4]",
                            "Willingness for effort, Likert item 6 [1,2,3,4]",
                            "Willingness for effort, Likert item 7 [1,2,3,4]",
                            "Instructors beliefs about the treatment, item 1 [1,2,3,4,5,6]",
                            "Instructors beliefs about the treatment, item 2 [1,2,3,4,5,6]"
                          ))

panderOptions('table.alignment.default', 'left')
pander(names_labels)
```

# Pre-treatment comparison

between the two treatment groups concerning...

## gender

```{r pre-treat: gender}

d_preT <- pbl_di %>%
  dplyr::filter(!is.na(geschl) & !is.na(treatment))

ttestBF(formula = geschl ~ treatment,
        data = d_preT)

```

## teaching experience

```{r pre-treat: teaching}

d_preT <- pbl_di %>%
  dplyr::filter(!is.na(unterrichtet) & !is.na(treatment))

ttestBF(formula = unterrichtet ~ treatment,
        data = d_preT)
```

## experience with video based analysis

```{r pre-treat: experience}
d_preT <- pbl_di %>%
  dplyr::filter(!is.na(erf_vid) & !is.na(treatment))

ttestBF(formula = erf_vid ~ treatment,
        data = d_preT)
```

## literature read

```{r pre-treat: literature}
d_preT <- pbl_di %>%
  dplyr::filter(!is.na(lit_pre) & !is.na(treatment))

ttestBF(formula = lit_pre ~ treatment,
        data = d_preT)

```

## prior knowledge

```{r pre-treat: prior}

d_preT <- pbl_di %>%
  dplyr::filter(!is.na(prior_knowledge) & !is.na(treatment))

ttestBF(formula = prior_knowledge ~ treatment,
        data = d_preT)

```

# Treatment check

Comparing several features between the treatment groups in both sessions respectively. Features are evaluated by trained raters attending and observing the instruction, disagreements were resolved through discussion.

## direct instruction from instructor

Should be different.  

__First session__

```{r }
treat_check <- rio::import(file = "data_public/rating-treatmentcheck.sav") %>%
  mutate(di_s1 = rowMeans(data.frame(B1_leitung_Doz1_u, B1_leitung_Doz2, B1_leitung_Doz3, B1_leitung_Doz4_u, B1_leitung_Doz5, B1_leitung_Doz6, B1_leitung_Doz7_u, B1_leitung_Doz8), na.rm = T),
         di_s2 = rowMeans(data.frame(B2_leitung_Doz1_u, B2_leitung_Doz2, B2_leitung_Doz3, B2_leitung_Doz4_u, B2_leitung_Doz5, B2_leitung_Doz6, B2_leitung_Doz7_u, B2_leitung_Doz8), na.rm = T),
         min_cases_s1 = B1_min_fallarb,
         min_cases_s2 = B2_min_fallarb,
         groups_s1 = B1_kleingruppen,
         groups_s2 = B2_kleingruppen,
         treatment = llm)

ttestBF(formula = di_s1 ~ treatment,
        data = treat_check)
```

__Second session__

```{r }
ttestBF(formula = di_s2 ~ treatment,
        data = treat_check)

```


## minutes spent on case-based learning

Should be equal.  

__First session__

```{r }
ttestBF(formula = min_cases_s1 ~ treatment,
        data = treat_check)
```

__Second session__

```{r }
ttestBF(formula = min_cases_s2 ~ treatment,
        data = treat_check)

```


## worked in small groups

Should be different.  

__First session__

```{r }
ttestBF(formula = groups_s1 ~ treatment,
        data = treat_check)
```

__Second session__

```{r , eval=F}
ttestBF(formula = groups_s2 ~ treatment,
        data = treat_check)

```

Vectors are constant (in the expected direction) that's why we can't compute a BF.


# Handle Missings

## Check for missingness

### Missing in data set

```{r }
# save variables for descriptive statistics later on
pbl_di_desc <- pbl_di %>%
  dplyr::select(treatment, attendance, 
         sel_att_pre1, sel_att_pre2, sel_att_pre3, sel_att_post1, sel_att_post2, sel_att_post3,
         theory_pre1, theory_pre2, theory_pre3, theory_post1, theory_post2, theory_post3, 
         inquiry_pre1, inquiry_pre2, inquiry_pre3, inquiry_post1, inquiry_post2, inquiry_post3, literature,
         doz_pass, doz_gef,
         geschl, unterrichtet, erf_vid, lit_pre, prior_knowledge)

# delete not needed for imputation
pbl_di <- pbl_di %>%
  dplyr::select(-c(unterrichtet, erf_vid, lit_pre, prior_knowledge))

vis_miss(pbl_di)
```

### Patterns of missingness

```{r }
gg_miss_upset(pbl_di)
```

## Decisions for imputation


### Number of imputations  
1000  

```{r n imput}
M <- 1000
```

### Imuptation model

for every variable

```{r }
pbl_di$sel_att_pre1 <- as.numeric(pbl_di$sel_att_pre1)
pbl_di$sel_att_pre2 <- as.numeric(pbl_di$sel_att_pre2)
pbl_di$sel_att_pre3 <- as.numeric(pbl_di$sel_att_pre3)
pbl_di$sel_att_post1 <- as.numeric(pbl_di$sel_att_post1)
pbl_di$sel_att_post2 <- as.numeric(pbl_di$sel_att_post2)
pbl_di$sel_att_post3 <- as.numeric(pbl_di$sel_att_post3)
pbl_di$T2_anstrT_4 <- as.numeric(pbl_di$T2_anstrT_4)
pbl_di$geschl[pbl_di$geschl == 3] <- NA
pbl_di <- pbl_di %>%
  mutate(geschl = ifelse(geschl == 2, 1, 0))


# Define table
model_tab <- data.frame(variable = c("treatment", "seminar", 
                                     "attendance", "sel_att_pre1", "sel_att_pre2", 
                                     "sel_att_pre3", "sel_att_post1","sel_att_post2", 
                                     "sel_att_post3", "theory_pre1", "theory_pre2", 
                                     "theory_pre3", "theory_post1", "theory_post2", 
                                     "theory_post3", "inquiry_pre1", "inquiry_pre2", 
                                     "inquiry_pre3", "inquiry_post1", "inquiry_post2", 
                                     "inquiry_post3", "literature", "T2_anstrS_1", 
                                     "T2_anstrS_2", "T2_anstrS_3", "T2_anstrT_1", 
                                     "T2_anstrT_2","T2_anstrT_3", "T2_anstrT_4", 
                                     "doz_pass", "doz_gef", "geschl"),
                        'scale type' = c("binary", "nominal",
                                         "metric", "metric", "metric",
                                         "metric", "metric", "metric",
                                         "metric", "metric", "metric",
                                         "metric", "metric", "metric",
                                         "metric", "metric", "metric",
                                         "metric", "metric", "metric",
                                         "metric", "metric", "metric",
                                         "metric", "metric", "metric",
                                         "metric", "metric", "metric",
                                         "metric", "metric", "binary"),
                        method = c("logreg", "polyreg",
                                   "pmm", "pmm", "pmm",
                                   "pmm", "pmm", "pmm",
                                   "pmm", "pmm", "pmm",
                                   "pmm", "pmm", "pmm",
                                   "pmm", "pmm", "pmm",
                                   "pmm", "pmm", "pmm",
                                   "pmm", "pmm", "pmm",
                                   "pmm", "pmm", "pmm",
                                   "pmm", "pmm", "pmm",
                                   "pmm", "pmm", "polyreg"))

ini <- mice(pbl_di, 
            maxit = 0, 
            m = M,
            seed = 666
            )

# Define methods

meth <- ini$method

meth[1:32] <- c("logreg", "polyreg",
                "pmm", "pmm", "pmm",
                "pmm", "pmm", "pmm",
                "pmm", "pmm", "pmm",
                "pmm", "pmm", "pmm",
                "pmm", "pmm", "pmm",
                "pmm", "pmm", "pmm",
                "pmm", "pmm", "pmm",
                "pmm", "pmm", "pmm",
                "pmm", "pmm", "pmm",
                "pmm", "pmm", "logreg")

pander(model_tab)
```


### Selection of predictors

We included the variables on `willingness for effort` for better prediction of missingness.  
  
Check for multicollinearity:

```{r corrgram}
corrgram(pbl_di, lower.panel = "panel.pie", upper.panel = "panel.cor")
```

The following variables are excluded as predictors: none.

```{r pred spec}
# set predictor specifications
pred <- ini$predictorMatrix
# pred[,"stunde"] <- 0 # stunde highly correlated with beg_hw_min

```


__variables that are function of other variables__  
None.  

__which variables to impute__  
All.  

__number of iterations__  
20  

```{r maxit}
maxit <- 20
```


## imputation

```{r imp, message=F, comment=F, warning=F, cache=F}
imp <- mice(pbl_di, 
            maxit = maxit, 
            m = M,
            meth = meth,
            pred = pred,
            seed = 666,
            printFlag = F
            )
```

## check imputation

__plausible values__  
of first 10 imputations

```{r plaus}
imp_conv <- mice(pbl_di, 
            maxit = maxit, 
            m = 10,
            meth = meth,
            pred = pred,
            seed = 666,
            printFlag = F
            )
lattice::stripplot(imp_conv, pch = 20, cex = 1.2)
```
  
  
All values seem plausible.
  
__check convergence__  

of first 10 imputations
```{r conv}
plot(imp_conv)
```


# Results

## Descriptive Statistics

Based on observed (and not imputed) data.  
__Group 0: DI__  


```{r descriptive 1}
# compute scales
pbl_di_desc <- pbl_di_desc %>%
  mutate(sel_att_pre = rowMeans(data.frame(sel_att_pre1, sel_att_pre2, sel_att_pre3), na.rm=T),
         sel_att_post = rowMeans(data.frame(sel_att_post1, sel_att_post2, sel_att_post3), na.rm=T),
         theory_pre = rowMeans(data.frame(theory_pre1, theory_pre2, theory_pre3), na.rm=T),
         theory_post = rowMeans(data.frame(theory_post1, theory_post2, theory_post3), na.rm=T),
         inquiry_pre = rowMeans(data.frame(inquiry_pre1, inquiry_pre2, inquiry_pre3), na.rm=T),
         inquiry_post = rowMeans(data.frame(inquiry_post1, inquiry_post2, inquiry_post3), na.rm=T)
         )

descr <- describeBy(pbl_di_desc, group = pbl_di_desc$treatment)

descr$`0`[2:10]
```

__Group 1: PBL__

```{r descriptive 2}
descr$`1`[2:10]
```

\

__Descriptive Plot 1__  
Differentiated by treatment and vignettes of pre and post test.
```{r descriptive plot 1}
# pivot data for plot
pbl_di_p <- pbl_di %>%
  dplyr::mutate(id = 1:length(sel_att_pre1)) %>%   # create id variable
  dplyr::select(id,treatment,
         sel_att_pre1, sel_att_pre2, sel_att_pre3, sel_att_post1, sel_att_post2, sel_att_post3,
         theory_pre1, theory_pre2, theory_pre3, theory_post1, theory_post2, theory_post3, 
         inquiry_pre1, inquiry_pre2, inquiry_pre3, inquiry_post1, inquiry_post2, inquiry_post3) %>%
  pivot_longer(cols = c(3:20),                                         # pivot longer first
               names_to = "variables",
               values_to = "values",
               values_transform = as.numeric) %>%
  dplyr::mutate(vignette = case_when(                                  # separate vignette number from variable name
                                variables == "sel_att_pre1" ~ "pre_1", 
                                variables == "sel_att_pre2" ~ "pre_2", 
                                variables == "sel_att_pre3" ~ "pre_3", 
                                variables == "sel_att_post1" ~ "post_1", 
                                variables == "sel_att_post2" ~ "post_2", 
                                variables == "sel_att_post3" ~ "post_3",
                                variables == "theory_pre1" ~ "pre_1", 
                                variables == "theory_pre2" ~ "pre_2", 
                                variables == "theory_pre3" ~ "pre_3", 
                                variables == "theory_post1" ~ "post_1", 
                                variables == "theory_post2" ~ "post_2", 
                                variables == "theory_post3" ~ "post_3",
                                variables == "inquiry_pre1" ~ "pre_1", 
                                variables == "inquiry_pre2" ~ "pre_2", 
                                variables == "inquiry_pre3" ~ "pre_3", 
                                variables == "inquiry_post1" ~ "post_1", 
                                variables == "inquiry_post2" ~ "post_2", 
                                variables == "inquiry_post3" ~ "post_3"),
                vignette = factor(vignette,
                                  levels = c("pre_1", "pre_2", "pre_3", "post_1", "post_2", "post_3")),
                variables = case_when(                                      # shorten variable names
                                variables == "sel_att_pre1" ~ "selection", 
                                variables == "sel_att_pre2" ~ "selection", 
                                variables == "sel_att_pre3" ~ "selection", 
                                variables == "sel_att_post1" ~ "selection", 
                                variables == "sel_att_post2" ~ "selection", 
                                variables == "sel_att_post3" ~ "selection",
                                variables == "theory_pre1" ~ "theory", 
                                variables == "theory_pre2" ~ "theory", 
                                variables == "theory_pre3" ~ "theory", 
                                variables == "theory_post1" ~ "theory", 
                                variables == "theory_post2" ~ "theory", 
                                variables == "theory_post3" ~ "theory",
                                variables == "inquiry_pre1" ~ "inquiry", 
                                variables == "inquiry_pre2" ~ "inquiry", 
                                variables == "inquiry_pre3" ~ "inquiry", 
                                variables == "inquiry_post1" ~ "inquiry", 
                                variables == "inquiry_post2" ~ "inquiry", 
                                variables == "inquiry_post3" ~ "inquiry")
                ) %>%
  pivot_wider(id_cols = c("id", "vignette", "treatment"),                                # then pivot back wide
              names_from = "variables", 
              values_from = "values") %>%
  dplyr::filter(!is.na(theory) | !is.na(inquiry)) %>%
  group_by(vignette, treatment) %>%
  dplyr::summarize(selection = mean(selection, na.rm = T),
                   inquiry = mean(inquiry, na.rm = T),
                   theory = mean(theory, na.rm = T)) %>%
  dplyr::mutate(prepost = case_when(vignette == "pre_1" | vignette == "pre_2" | vignette == "pre_3" ~ "pre",
                                    vignette == "post_1" | vignette == "post_2" | vignette == "post_3" ~ "post")) %>%
  ungroup()



p <-
ggplot(pbl_di_p, aes(x = inquiry, y = theory)) +
  # stat_density_2d(aes(fill = stat(level)), geom = "polygon", alpha = .3, h = c(1.2,1.2), show.legend = F) +
  # scale_fill_viridis_c() +
  geom_point(aes(color=vignette, shape = factor(treatment, labels = c("DI", "PBL"))), size = 4) +
  theme_few() +
  scale_shape_manual(values = c(12,15)) +
  scale_color_manual(values = c("#00B6D6", "#0B51E3", "#0AD182",
                               "#D60E00", "#D10A9E", "#FF620D")) +
  scale_fill_manual(values = c("#00B6D6", "#0B51E3", "#0AD182",
                               "#D60E00", "#D10A9E", "#FF620D")) +
  scale_y_continuous(limits = c(0,.5), breaks = c(0,.1,.2,.3,.4,.5), minor_breaks = NULL, expand = c(0, 0)) +
  scale_x_continuous(limits = c(0,3), breaks = c(0,1,2,3), minor_breaks = NULL, expand = c(0, 0)) +
  xlab("Realized inquiry steps in analyses") +
  ylab("% of analyses containing theory-practice integration")
  
p$labels$shape <- "treatment"
# ggsave("Fig2.tiff", width = 90, height = 70, units = "mm", dpi = 500, scale = 1.6)

p

```



\

__Descriptive Plot 2__  
Change from pretest to posttest on realizes inquiry steps and theory-practice integration differentiated by treatment.
```{r descriptive plot 2}
pbl_di_p2 <- pbl_di %>%
  mutate(id = 1:nrow(.),
         theory_pre1 = as.numeric(theory_pre1),
         theory_pre2 = as.numeric(theory_pre2),
         theory_pre3 = as.numeric(theory_pre3),
         theory_post1 = as.numeric(theory_post1),
         theory_post2 = as.numeric(theory_post2),
         theory_post3 = as.numeric(theory_post3),
         theory_pre = rowMeans(data.frame(theory_pre1, theory_pre2, theory_pre3)),
         theory_pos = rowMeans(data.frame(theory_post1, theory_post2, theory_post3)),
         inquir_pre = rowMeans(data.frame(inquiry_pre1, inquiry_pre2, inquiry_pre3)),
         inquir_pos = rowMeans(data.frame(inquiry_post1, inquiry_post2, inquiry_post3)),
         theory = theory_pos - theory_pre,
         inquiry = inquir_pos - inquir_pre) %>%
  dplyr::select(id, treatment, theory, inquiry)


pbl_di_p2$treatment <- factor(pbl_di_p2$treatment, 
                              levels = c(0,1), 
                              labels = c("DI", "PB"))


ggplot(pbl_di_p2, aes(x = inquiry, y = theory)) +
  stat_density_2d(aes(fill = ..level..), geom = "polygon")  +
  scale_fill_continuous(type = "viridis") +
  scale_y_continuous(limits = c(-1.1,1.1), labels = c("-100%", "-50%", "0%", "+50%", "+100%"), 
                     minor_breaks = NULL, expand = c(0, 0)) +
  scale_x_continuous(limits = c(-3.1,3.1), breaks = c(-3,-2,-1,0,1,2,3), 
                     labels = c("-3", "-2", "-1", "0", "+1", "+2", "+3"), 
                     minor_breaks = NULL, expand = c(0, 0)) +
  xlab("change in realized inquiry steps in analyses") +
  ylab("change in % of analyses \ncontaining theory-practice integration") +
  labs(fill = "density") +
  geom_hline(yintercept=0, color = "white", alpha = .2) +
  geom_vline(xintercept=0, color = "white", alpha = .2) +
  theme_bw() +
  facet_wrap(~treatment)
```


\

__Descriptive Plot 3__  
Change from pretest to posttest in theory-practice integrations plotted with the instructor's positive attitude.
```{r descriptive plot 3}
pbl_di_p3 <- pbl_di %>%
  mutate(doz = rowMeans(data.frame(doz_pass, doz_gef), na.rm = T),
         theory_pre = rowMeans(data.frame(theory_pre1, theory_pre2, theory_pre3), na.rm = T),
         theory_post = rowMeans(data.frame(theory_post1, theory_post2, theory_post3), na.rm = T),
         theory_change = theory_post - theory_pre) %>%
  dplyr::select(doz, treatment, theory_pre, theory_post, theory_change) %>%
  pivot_longer(cols=3:5, names_to = "time", values_to = "theory")


ggplot(pbl_di_p3%>%dplyr::filter(time=="theory_change"), aes(x=doz, y=theory)) +
  stat_density_2d(aes(fill = ..level..), geom = "polygon")  +
  geom_smooth(method='lm', color = "red") +
  scale_fill_continuous(type = "viridis") +
  scale_y_continuous(limits = c(-.5,1.2), 
                     expand = c(0,0), 
                     breaks = c(-.4, -.2, 0,.2,.4,.6,.8,1),
                     labels = c("-40%", "-20%", "0%", "+20%", "+40%", "+60%", "+80%", "+100%")
                     ) +
  scale_x_continuous(limits = c(0.5,7), 
                     expand = c(0,0), 
                     breaks = c(1:6)) +
  geom_xsidedensity(aes(y=stat(density)), fill = "#37678c", color = NA) +
  geom_ysidedensity(aes(x=stat(density)), fill = "#37678c", color = NA, scale = "free_y") +
  scale_ysidex_continuous() +
  scale_xsidey_continuous() +
  xlab("instructor's positive attitude") +
  ylab("change in % of analyses \ncontaining theory-practice integration") +
  labs(fill = "density") +
  theme_bw()

```


## Inference Statistics

Based on imputed data.

### Hypothesis 1: DV 'selection'

```{r selection}

mulest <- matrix(0,
                 nrow=1000,
                 ncol=2
                 )
covwithin <- matrix(0,
                    nrow=2,
                    ncol=2
                    )

# execute 1000 multiple regressions using the imputed data matrices and store the estimates 
# of only the regression coefficients of funumb on prenumb and postnumband and the average 
# of the 1000 covariance matrices.
# See Hoijtink, Gu, Mulder, and Rosseel (2019) for an explanation of the latter.
model <- '
          select_t1 =~ sel_att_pre1 + sel_att_pre2 + sel_att_pre3
  
          select_t2 =~ sel_att_post1 + sel_att_post2 + sel_att_post3
  
          instr_beliefs =~ lamda*doz_pass + lamda*doz_gef
          
          select_t2 ~ select_t1 + treatment + instr_beliefs + literature + attendance
         '

fit_mean <- data.frame(chi_sq = c(),
                       chi_df = c(),
                       chi_p = c(),
                       cfi_robust = c(),
                       tli_robust = c(),
                       rmsea_robust = c(),
                       rmsea_cilower_robust = c(),
                       rmsea_ciupper_robust = c())

for(i in 1:M) {
  # compute model
  fit <- sem(model = model,
             data = complete(imp,i),
             cluster = "seminar",
             se = "robust",
             orthogonal = T,
             std.lv = T
             )
  
  # save coefficients
  mulest[i,]<-coef(fit)[10:11]
  covwithin<-covwithin + 1/M * vcov(fit)[10:11,10:11]
  
  # save fit indices
  fit_mean[i, "chi_sq"] <- fitMeasures(fit)[6]
  fit_mean[i, "chi_df"] <- fitMeasures(fit)[7]
  fit_mean[i, "chi_p"] <- fitMeasures(fit)[8]
  fit_mean[i, "cfi_robust"] <- fitMeasures(fit)[27]
  fit_mean[i, "tli_robust"] <- fitMeasures(fit)[28]
  fit_mean[i, "rmsea_robust"] <- fitMeasures(fit)[48]
  fit_mean[i, "rmsea_cilower_robust"] <- fitMeasures(fit)[49]
  fit_mean[i, "rmsea_ciupper_robust"] <- fitMeasures(fit)[50]
}


# average fit indices
fit_mean <- fit_mean %>%
  dplyr::summarize_all(mean)

fit_mean

# Compute the average of the estimates and assign names, the between and total covariance matrix.
# See Hoijtink, Gu, Mulder, and Rosseel (2019) for an explanation.
estimates <- colMeans(mulest)
names(estimates) <- c("treatment", "instr_beliefs")
covbetween <- cov(mulest)
covariance <- covwithin + (1+1/M)*covbetween

# determine the sample size
samp <- nrow(pbl_di)

# compute the effective sample size
# See Hoijtink, Gu, Mulder, and Rosseel (2019) for an explanation.
nucom<-samp-length(estimates)
lam <- (1+1/M)*(1/length(estimates))* sum(diag(covbetween %*% ginv(covariance)))
nuold<-(M-1)/(lam^2)
nuobs<-(nucom+1)/(nucom+3)*nucom*(1-lam)
nu<- nuold*nuobs/(nuold+nuobs)
fracmis <- (nu+1)/(nu+3)*lam + 2/(nu+3)
neff<-samp-samp*fracmis
covariance<-list(covariance)

# set the seed
set.seed(100)
# test hypotheses with bain
results <- bain(estimates,
                "instr_beliefs>0 & treatment=0;
                instr_beliefs<0 & treatment=0;
                instr_beliefs=0 & treatment=0",
                n=neff,
                Sigma=covariance,
                group_parameters=2,
                joint_parameters = 0)
# display the results
print(results)

# display BFs of Hypotheses against each other
results$BFmatrix
```


### Hypothesis 2: DV 'inquiry'

```{r inquiry}
mulest <- matrix(0,
                 nrow=1000,
                 ncol=2
                 )
covwithin <- matrix(0,
                    nrow=2,
                    ncol=2
                    )

# execute 1000 multiple regressions using the imputed data matrices and store the estimates 
# of only the regression coefficients of funumb on prenumb and postnumband and the average 
# of the 1000 covariance matrices.
# See Hoijtink, Gu, Mulder, and Rosseel (2019) for an explanation of the latter.
model <- '
          inquiry_t1 =~ inquiry_pre1 + inquiry_pre2 + inquiry_pre3
  
          inquiry_t2 =~ inquiry_post1 + inquiry_post2 + inquiry_post3
  
          instr_beliefs =~ lamda*doz_pass + lamda*doz_gef
          
          inquiry_t2 ~ inquiry_t1 + treatment + instr_beliefs + literature + attendance
         '

fit_mean <- data.frame(chi_sq = c(),
                       chi_df = c(),
                       chi_p = c(),
                       cfi_robust = c(),
                       tli_robust = c(),
                       rmsea_robust = c(),
                       rmsea_cilower_robust = c(),
                       rmsea_ciupper_robust = c())

for(i in 1:M) {
  # compute model
  fit <- sem(model = model,
             data = complete(imp,i),
             cluster = "seminar",
             se = "robust",
             orthogonal = T,
             std.lv = T
             )
  
  # save coefficients
  mulest[i,]<-coef(fit)[10:11]
  covwithin<-covwithin + 1/M * vcov(fit)[10:11,10:11]
  
  # save fit indices
  fit_mean[i, "chi_sq"] <- fitMeasures(fit)[6]
  fit_mean[i, "chi_df"] <- fitMeasures(fit)[7]
  fit_mean[i, "chi_p"] <- fitMeasures(fit)[8]
  fit_mean[i, "cfi_robust"] <- fitMeasures(fit)[27]
  fit_mean[i, "tli_robust"] <- fitMeasures(fit)[28]
  fit_mean[i, "rmsea_robust"] <- fitMeasures(fit)[48]
  fit_mean[i, "rmsea_cilower_robust"] <- fitMeasures(fit)[49]
  fit_mean[i, "rmsea_ciupper_robust"] <- fitMeasures(fit)[50]
}


# average fit indices
fit_mean <- fit_mean %>%
  dplyr::summarize_all(mean)

fit_mean


# Compute the average of the estimates and assign names, the between and total covariance matrix.
# See Hoijtink, Gu, Mulder, and Rosseel (2019) for an explanation.
estimates <- colMeans(mulest)
names(estimates) <- c("treatment", "instr_beliefs")
covbetween <- cov(mulest)
covariance <- covwithin + (1+1/M)*covbetween

# determine the sample size
samp <- nrow(pbl_di)

# compute the effective sample size
# See Hoijtink, Gu, Mulder, and Rosseel (2019) for an explanation.
nucom<-samp-length(estimates)
lam <- (1+1/M)*(1/length(estimates))* sum(diag(covbetween %*% ginv(covariance)))
nuold<-(M-1)/(lam^2)
nuobs<-(nucom+1)/(nucom+3)*nucom*(1-lam)
nu<- nuold*nuobs/(nuold+nuobs)
fracmis <- (nu+1)/(nu+3)*lam + 2/(nu+3)
neff<-samp-samp*fracmis
covariance<-list(covariance)

# set the seed
set.seed(100)
# test hypotheses with bain
results <- bain(estimates,
                "treatment>0 & instr_beliefs>0;
                treatment=0 & instr_beliefs>0;
                treatment>0 & instr_beliefs=0;
                treatment=0 & instr_beliefs=0;",
                n=neff,
                Sigma=covariance,
                group_parameters=2,
                joint_parameters = 0)
# display the results
print(results)

# display BFs of Hypotheses against each other
results$BFmatrix
```




### Hypothesis 3: DV 'theory'

```{r theory}
mulest <- matrix(0,
                 nrow=1000,
                 ncol=2
                 )
covwithin <- matrix(0,
                    nrow=2,
                    ncol=2
                    )

# execute 1000 multiple regressions using the imputed data matrices and store the estimates 
# of only the regression coefficients of funumb on prenumb and postnumband and the average 
# of the 1000 covariance matrices.
# See Hoijtink, Gu, Mulder, and Rosseel (2019) for an explanation of the latter.
model <- '
          theory_t1 =~ theory_pre1 + theory_pre2 + theory_pre3
  
          theory_t2 =~ theory_post1 + theory_post2 + theory_post3
  
          instr_beliefs =~ lamda*doz_pass + lamda*doz_gef
          
          theory_t2 ~ theory_t1 + treatment + instr_beliefs + literature + attendance
         '

fit_mean <- data.frame(chi_sq = c(),
                       chi_df = c(),
                       chi_p = c(),
                       cfi_robust = c(),
                       tli_robust = c(),
                       rmsea_robust = c(),
                       rmsea_cilower_robust = c(),
                       rmsea_ciupper_robust = c())

for(i in 1:M) {
  # compute model
  fit <- sem(model = model,
             data = complete(imp,i),
             cluster = "seminar",
             se = "robust",
             orthogonal = T,
             std.lv = T
             )
  
  # save coefficients
  mulest[i,]<-coef(fit)[10:11]
  covwithin<-covwithin + 1/M * vcov(fit)[10:11,10:11]
  
  # save fit indices
  fit_mean[i, "chi_sq"] <- fitMeasures(fit)[6]
  fit_mean[i, "chi_df"] <- fitMeasures(fit)[7]
  fit_mean[i, "chi_p"] <- fitMeasures(fit)[8]
  fit_mean[i, "cfi_robust"] <- fitMeasures(fit)[27]
  fit_mean[i, "tli_robust"] <- fitMeasures(fit)[28]
  fit_mean[i, "rmsea_robust"] <- fitMeasures(fit)[48]
  fit_mean[i, "rmsea_cilower_robust"] <- fitMeasures(fit)[49]
  fit_mean[i, "rmsea_ciupper_robust"] <- fitMeasures(fit)[50]
}


# average fit indices
fit_mean <- fit_mean %>%
  dplyr::summarize_all(mean)

fit_mean


# Compute the average of the estimates and assign names, the between and total covariance matrix.
# See Hoijtink, Gu, Mulder, and Rosseel (2019) for an explanation.
estimates <- colMeans(mulest)
names(estimates) <- c("treatment", "instr_beliefs")
covbetween <- cov(mulest)
covariance <- covwithin + (1+1/M)*covbetween

# determine the sample size
samp <- nrow(pbl_di)

# compute the effective sample size
# See Hoijtink, Gu, Mulder, and Rosseel (2019) for an explanation.
nucom<-samp-length(estimates)
lam <- (1+1/M)*(1/length(estimates))* sum(diag(covbetween %*% ginv(covariance)))
nuold<-(M-1)/(lam^2)
nuobs<-(nucom+1)/(nucom+3)*nucom*(1-lam)
nu<- nuold*nuobs/(nuold+nuobs)
fracmis <- (nu+1)/(nu+3)*lam + 2/(nu+3)
neff<-samp-samp*fracmis
covariance<-list(covariance)

# set the seed
set.seed(100)
# test hypotheses with bain
results <- bain(estimates,
                "treatment>0 & instr_beliefs>0;
                treatment=0 & instr_beliefs>0;
                treatment>0 & instr_beliefs=0;
                treatment=0 & instr_beliefs=0;",
                n=neff,
                Sigma=covariance,
                group_parameters=2,
                joint_parameters = 0
                )
# display the results
print(results)

# display BFs of Hypotheses against each other
results$BFmatrix
```
